---
title: Schedule
---

```{r}

library(kableExtra)
library(glue)
library(here)
library(tidyverse)

here("scripts/functions.R") %>% 
  source()

# For indicating which nests require a selfie stick:

high_nests <-
  here("data", "field_data.rds") %>% 
  read_rds() %>% 
  pluck("nests") %>% 
  filter(height > 2) %>% 
  pull(nest_id) %>% 
  str_c(collapse = "|") %>% 
  str_c("(", ., ")")

next_nest_checks <-
  here("data", "temp_nest_checking.rds") %>% 
  read_rds() %>% 
  
  # Add emoji for selfie-stick nests:
  
  mutate(
    check_nests = 
      str_replace_all(
        check_nests,
        high_nests,
        "\\1 \U1F992"
      )
  )

next_pred_cam_maintenance <-
  here("data", "predator_camera_maintenance.rds") %>% 
  read_rds() %>% 
  mutate(
    patch,
    date = next_maintenance,
    camera_id = 
      str_extract_all(camera_id, "[0-2]$"),
    .keep = "none"
  ) %>% 
    summarize(
      predator_cameras = 
        str_flatten(camera_id, collapse = ", "),
      .by = !camera_id
    )

schedule <- 
  here("data", "season_schedule.rds") %>% 
  read_rds() %>% 
  unnest(patch_counts) %>% 
  unnest(boards) %>% 
  filter(
    week ==
        week(
        today() + 1
      ) - 19,
  ) %>% 
  summarize(
    boards = 
      str_flatten(board_id, collapse = ", "),
    .by = !board_id
  ) %>% 
  left_join(
    next_nest_checks,
    by = join_by(date == date, patch_count == patch)
  ) %>% 
  left_join(
    next_pred_cam_maintenance,
    by = join_by(date, patch_count == patch)
  ) %>% 
  mutate(
    departure_time = 
      (
        hm(arrive) - minutes(45)
      ) %>% 
      hms::hms() %>% 
      as.character() %>% 
      str_remove(":00$"),
    across(
      check_nests:predator_cameras,
      ~ replace_na(.x, "-")
    )
  )

schedule_list <-
  schedule %>% 
  split(schedule$day)

day_level_data <-
  schedule_list %>% 
  map(
    ~ .x %>% 
      select(
          date,
          arrive:helper
        ) %>% 
        distinct() %>% 
      mutate(
        date_pretty = make_pretty_dates(date)
      )
  )

# custom functions --------------------------------------------------------

my_kable_style <-
  function(.kable) {
    .kable %>% 
      kable_styling(
        bootstrap_options = 
          c(
            "striped",
            "hover",
            "condensed"
          ),
        full_width = FALSE,
        font_size = 28
      )
  }

# Departure, arrival, and sunrise table:

morning_times <- 
  function(.day) {
    schedule_list %>% 
      pluck(.day) %>% 
      distinct(
        "Departure" = departure_time, 
        "Arrival" = arrive, 
        "Sunrise" = sunrise
      ) %>% 
      kable(
        format = "html",
        align = 
          c("c", "c", "c")
      ) %>% 
      my_kable_style() %>% 
      column_spec(1:3, width = "14.5em")
  }

# Format point counts and coverboards for a given day:

pred_counts <- 
  function(.day) {
      schedule_list %>% 
        pluck(.day) %>% 
        mutate(
          Patch = patch_count,
          Time = 
            str_c(date, sunrise) %>% 
            {
              ymd_hm(.) + 
                minutes(40 * (patch_order - 1))
            } %>% 
            format("%H:%M")
        ) %>% 
      select(
        Time,
        Patch = patch_count,
        Coverboards = boards,
        `Check nests` = check_nests,
        `Predator cameras` = predator_cameras
      ) %>% 
      kable(
        format = "html",
        align =
          c(
            "c",
            "l",
            "c",
            "l"
          )
      ) %>% 
      my_kable_style()
  }

# Nest searching order:

nest_searching_order <-
  function(
    .day,
    .ordered = TRUE,
    .patches
  ) {
    if(.ordered) {
      schedule_list %>%
        pluck(.day) %>%
        filter(patch_order != 1) %>%
        arrange(
          desc(patch_order)
        ) %>%
        pull(patch_count) %>%
        str_flatten(collapse = " \u2192 ")
    } else {
      .patches %>% 
        str_flatten(collapse = " \u2192 ")
    }
  }

# Nest searching activity details:

nest_searching <- 
  function(
    .day = "Tue",
    .ordered = TRUE,
    .helper,
    .patches,
    .helper_patch_1 = "-",
    .me_patch_1 = "-",
    .helper_patch_2 = "-",
    .me_patch_2 = "-"
  ) {
    if(.ordered) {
      start <- 
        schedule_list %>% 
        pluck(.day) %>% 
        filter(patch_order != 1) %>% 
        arrange(
          desc(patch_order)
        ) %>% 
        select(helper, patch_count) %>% 
        mutate(
          patch_count =
            factor(
              patch_count,
              levels = 
                patch_count
            )
        )
    } else {
      start <- 
        tibble(
          helper = .helper,
          patch_count = .patches
        ) %>% 
        mutate(
          patch_count =
            factor(
              patch_count,
              levels = 
                patch_count
            )
        )
    }
    
    crossing(
      Patch = start$patch_count,
      Person = 
        c(
          "TNS",
          pull(start, unique(helper))
        )
    ) %>% 
      mutate(
        Activities = 
          c(
            .helper_patch_1,
            .me_patch_1,
            .helper_patch_2,
            .me_patch_2
          )
      ) %>% 
      filter(
        Person != "-"
      ) %>% 
      kable(format = "html") %>% 
      # my_kable_style() %>% 
      collapse_rows(
        columns = 1
      )
  }
```

# Weekly schedule: `r pretty_date_range(schedule)`

<div class="accordion-group" data-open-today="true">

<button 
  class="accordion"
  data-date="`r day_level_data$Mon$date`">
  Monday `r day_level_data$Mon$date_pretty`
</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Mon$helper)`*

```{r}
morning_times(.day = "Mon")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Mon")
```

**Nest searching**: `r nest_searching_order(.day = "Mon")`

```{r}
nest_searching(
  .day = "Mon",
  .me_patch_1 = "Continue path down the Western edge; Create distributaries from the central N-S path",
  .me_patch_2 = "Search near CB 1 and 2 -- carve paths where necessary",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .patches = c("", ""),
  # .helper = "",
  # .helper_patch_1 = "-",
  # .helper_patch_2 = "-"
)
```

Other to-dos:

* GPS the path at coyote from CB 4 to CB 5. 
* Grab extra poles from grassland_a and the old forest_b.

:::

<button 
  class="accordion"
  data-date="`r day_level_data$Tue$date`">
  Tuesday `r day_level_data$Tue$date_pretty`
</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Tue$helper)`*

```{r}
morning_times(.day = "Tue")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Tue")
```

**Nest searching**: `r nest_searching_order(.day = "Tue")`

```{r}
nest_searching(
  .day = "Tue",
  .helper_patch_1 = "-",
  .me_patch_1 = "-",
  .helper_patch_2 = "-",
  .me_patch_2 = "-",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .helper = "",
  # .patches = c("", "")
)
```

:::

<button 
  class="accordion"
  data-date="`r day_level_data$Wed$date`">
  Wednesday `r day_level_data$Wed$date_pretty`
</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Wed$helper)`*

```{r}
morning_times(.day = "Wed")
```

:::

**Point count times, coverboards, and nests to check**:

*BSE: Machete a trail at firehouse that connects trailcam_1 and the northwest passage. There is a fence near trailcam_1 that can be navigated around, but bring boltcutters just in case.*

```{r}
pred_counts(.day = "Wed")
```

**Nest searching**: `r nest_searching_order(.day = "Wed")`

```{r}
nest_searching(
  .day = "Wed",
  .me_patch_1 = "-",
  .me_patch_2 = "-",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .patches = c("", ""),
  .helper = "BSE",
  .helper_patch_1 = "-",
  .helper_patch_2 = "-"
)
```

:::

<button 
  class="accordion"
  data-date="`r day_level_data$Thu$date`">
  Thursday `r day_level_data$Thu$date_pretty`
</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Thu$helper)`*

```{r}
morning_times(.day = "Thu")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Thu")
```

*Note: Install trailcam_2 at witch_hazel.*

**Nest searching**: `r nest_searching_order(.day = "Thu")`

```{r}
nest_searching(
  .day = "Thu",
  .helper_patch_1 = "-",
  .me_patch_1 = "-",
  .helper_patch_2 = "-",
  .me_patch_2 = "-",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .helper = "",
  # .patches = c("", "")
)
```

*Note: There is an active nest right along the power line alley walkway at firehouse... be very careful when traversing through that area!*

:::

<button 
  class="accordion"
  data-date="`r day_level_data$Fri$date`">
  Friday `r day_level_data$Fri$date_pretty`
</button>

::: panel

::: summary_box

*Helper: BSE*
<!-- `r unique(schedule_list$Fri$helper)`* -->

```{r}
morning_times(.day = "Fri")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Fri")
```

*BSE: Complete the circle at grassland_b during morning sampling. Then extend a path from the circle to the Southern end of the patch.*

**Nest searching**: `r nest_searching_order(.day = "Fri")`

```{r}
nest_searching(
  .day = "Fri",
  .me_patch_1 = "Search the CB 6 end of the patch and create distributaries from the main path",
  .me_patch_2 = "Continue path from the South end of the patch to the trailcam_0 trail; Create distributaries along the main paths",
  
  # If schedule changes:
  
  .ordered = FALSE,
  .patches = c("grassland_a", "grassland_b_fence"),
  .helper = "BSE",
  .helper_patch_1 = "Connector trail from CB 1 to the trailcam_1 path",
  .helper_patch_2 = "Extend the main cross-path patch further NE (starting at the path that begins between CB 4 and 5)"
)
```

Notes:

* At each nest, take a picture from further away and jot down a brief description of where the picture was taken and how to find the nest.
* Install metal boxes at trailcam_0 in each patch

:::

<button 
  class="accordion"
  data-date="`r day_level_data$Sat$date`">
  Saturday `r day_level_data$Sat$date_pretty`
</button>

::: panel

::: summary_box

*Helper: -*
<!-- `r unique(schedule_list$Sat$helper)`* -->

```{r}
morning_times(.day = "Sat")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Sat")
```

**Nest searching**: `r nest_searching_order(.day = "Sat")`

```{r}
nest_searching(
  .day = "Sat",
  # .helper_patch_1 = "-",
  .me_patch_1 = "Pocket along entrace path",
  # .helper_patch_2 = "-",
  .me_patch_2 = "Line of trees at the Southern end of the patch",
  
  # If schedule changes:
  
  .ordered = FALSE,
  .helper = "-",
  .patches = c("leech", "grassland_b")
)
```

*Note: There are two active nest in the Southern portion of grassland_b... be very careful when traversing (or macheteing) through that area!*

:::

</div>
