---
format: 
  html:
    self-contained: true
    standalone: true
    number-sections: false
    search: true
    theme: cosmo
    css: custom_style.scss
editor: source
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false

library(kableExtra)
library(tidyverse)

schedule <- 
  read_rds("data/season_schedule.rds") %>% 
  filter(week == 3)

# custom functions --------------------------------------------------------

my_kable_style <-
  function(.kable) {
    .kable %>% 
      kable_styling(
        bootstrap_options = 
          c(
            "striped",
            "hover",
            "condensed"
          ),
        full_width = FALSE,
        font_size = 28
      )
  }

# Format point counts and coverboards for a given day:

pred_counts <- 
  function(.day) {
    schedule %>% 
      filter(day == .day) %>% 
      unnest(patch_counts) %>% 
      unnest(boards) %>% 
      mutate(
        Patch = patch_count,
        board_num = 
          rep_len(
            c("board_1", "board_2"),
            n()
          )
      ) %>% 
      pivot_wider(
        names_from = board_num,
        values_from = board_id
      ) %>% 
      unite(
        "Coverboards",
        board_1:board_2,
        sep = ", "
      ) %>% 
      mutate(
        Time =
          str_c(date, sunrise, sep = " ") %>% 
          ymd_hm(),
        Time = 
          case_when(
            patch_order == 2 ~
              Time + minutes(40),
            patch_order == 3 ~
              Time + minutes(80),
            TRUE ~ Time
          ) %>% 
          hms::as_hms() %>%
          as.character() %>% 
          str_remove(":00$")
      ) %>% 
      select(
        Time,
        Patch,
        Coverboards
      ) %>% 
      kable(
        align =
          c(
            "c",
            "l",
            "c"
          )
      ) %>% 
      my_kable_style()
  }

# Nest searching order:

nest_searching <- 
  function(.day) {
    schedule %>% 
      filter(day == .day) %>% 
      unnest(patch_counts) %>% 
      arrange(
        desc(patch_order)
      ) %>% 
      pull(patch_count) %>% 
      str_flatten(collapse = " \u2192 ")
  }

```

:::{style="margin-bottom: 0px"}
# Weekly schedule
:::

:::{style="margin-top: 0px"}
### `r min(schedule$date)` - `r max(schedule$date)`
:::

We will arrive at dawn to have time for set-up and travel to the point count location. The first point count starts at sunrise. We will arrive at the point count location a few minutes before then to let the birds settle down before beginning.

## Monday (`r filter(schedule, day == "Mon") %>% pull(date)`)

*Helper: `r filter(schedule, day == "Mon") %>% pull(helper)`*

**Arrival**: `r filter(schedule, day == "Mon") %>% pull(arrive)`

**Sunrise**: `r filter(schedule, day == "Mon") %>% pull(sunrise)`

<div style="margin-bottom: 0px">
**Point counts and coverboards**:
</div>

:::{style="margin-bottom: 100px"}
```{r}
#| echo: false
#| eval: true
 
pred_counts(.day = "Tue")
 
```
:::

<div style="margin-top: 10px">
**Nest monitoring**:
</div>

**Nest searching**: `r nest_searching(.day = "Mon")`

## Tuesday (`r filter(schedule, day == "Tue") %>% pull(date)`)

*Helper: `r filter(schedule, day == "Tue") %>% pull(helper)`*

**Arrival**: `r filter(schedule, day == "Tue") %>% pull(arrive)`

**Sunrise**: `r filter(schedule, day == "Tue") %>% pull(sunrise)`

**Point counts and coverboards**:

```{r}
#| echo: false
#| eval: true

pred_counts(.day = "Tue")

```

**Nest monitoring**:

**Nest searching**: `r nest_searching(.day = "Tue")`

## Wednesday (`r filter(schedule, day == "Wed") %>% pull(date)`)

*Helper: `r filter(schedule, day == "Wed") %>% pull(helper)`*

**Arrival**: `r filter(schedule, day == "Wed") %>% pull(arrive)`

**Sunrise**: `r filter(schedule, day == "Wed") %>% pull(sunrise)`

**Point counts and coverboards**:

```{r}
#| echo: false
#| eval: true

pred_counts(.day = "Wed")

```

**Nest monitoring**:

**Nest searching**: `r nest_searching(.day = "Wed")`

## Thursday (`r filter(schedule, day == "Thu") %>% pull(date)`)

*Helper: `r filter(schedule, day == "Thu") %>% pull(helper)`*

**Arrival**: `r filter(schedule, day == "Thu") %>% pull(arrive)`

**Sunrise**: `r filter(schedule, day == "Thu") %>% pull(sunrise)`

**Point counts and coverboards**:

```{r}
#| echo: false
#| eval: true

pred_counts(.day = "Thu")

```

**Nest monitoring**:

**Nest searching**: `r nest_searching(.day = "Thu")`

## Friday (`r filter(schedule, day == "Fri") %>% pull(date)`)

*Helper: `r filter(schedule, day == "Fri") %>% pull(helper)`*

**Arrival**: `r filter(schedule, day == "Fri") %>% pull(arrive)`

**Sunrise**: `r filter(schedule, day == "Fri") %>% pull(sunrise)`

**Point counts and coverboards**:

```{r}
#| echo: false
#| eval: true

pred_counts(.day = "Fri")

```

**Nest monitoring**:

**Nest searching**: `r nest_searching(.day = "Fri")`

## Saturday (`r filter(schedule, day == "Sat") %>% pull(date)`)

*Helper: `r filter(schedule, day == "Sat") %>% pull(helper)`*

**Arrival**: `r filter(schedule, day == "Sat") %>% pull(arrive)`

**Sunrise**: `r filter(schedule, day == "Sat") %>% pull(sunrise)`

**Point counts and coverboards**:

```{r}
#| echo: false
#| eval: true

pred_counts(.day = "Sat")

```

**Nest monitoring**:

**Nest searching**: `r nest_searching(.day = "Sat")`
