---
format: html
pagetitle: schedule
editor: source
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
  message: false
---

```{r}

library(kableExtra)
library(glue)
library(here)
library(tidyverse)

here("scripts/functions.R") %>% 
  source()

next_nest_checks <-
  here("data", "temp_nest_checking.rds") %>% 
  read_rds()

next_pred_cam_maintenance <-
  here("data", "predator_camera_maintenance.rds") %>% 
  read_rds() %>% 
  mutate(
    patch,
    date = next_maintenance,
    camera_id = 
      str_extract_all(camera_id, "[0-2]$"),
    .keep = "none"
  ) %>% 
    summarize(
      predator_cameras = 
        str_flatten(camera_id, collapse = ", "),
      .by = !camera_id
    )

schedule <- 
  here("data", "season_schedule.rds") %>% 
  read_rds() %>% 
  unnest(patch_counts) %>% 
  unnest(boards) %>% 
  filter(
    week ==
        week(
        today() + 1
      ) - 19,
  ) %>% 
  summarize(
    boards = 
      str_flatten(board_id, collapse = ", "),
    .by = !board_id
  ) %>% 
  left_join(
    next_nest_checks,
    by = join_by(date == date, patch_count == patch)
  ) %>% 
  left_join(
    next_pred_cam_maintenance,
    by = join_by(date, patch_count == patch)
  ) %>% 
  mutate(
    departure_time = 
      (
        hm(arrive) - minutes(45)
      ) %>% 
      hms::hms() %>% 
      as.character() %>% 
      str_remove(":00$"),
    across(
      check_nests:predator_cameras,
      ~ replace_na(.x, "-")
    )
  )

schedule_list <-
  schedule %>% 
  split(schedule$day)

day_level_data <-
  schedule_list %>% 
  map(
    ~ .x %>% 
      select(
          date,
          arrive:helper
        ) %>% 
        distinct() %>% 
      mutate(
        date_pretty = make_pretty_dates(date)
      )
  )

# custom functions --------------------------------------------------------

my_kable_style <-
  function(.kable) {
    .kable %>% 
      kable_styling(
        bootstrap_options = 
          c(
            "striped",
            "hover",
            "condensed"
          ),
        full_width = FALSE,
        font_size = 28
      )
  }

# Departure, arrival, and sunrise table:

morning_times <- 
  function(.day) {
    schedule_list %>% 
      pluck(.day) %>% 
      distinct(
        "Departure" = departure_time, 
        "Arrival" = arrive, 
        "Sunrise" = sunrise
      ) %>% 
      kable(
        align = 
          c("c", "c", "c")
      ) %>% 
      my_kable_style()
  }

# Format point counts and coverboards for a given day:

pred_counts <- 
  function(.day) {
      schedule_list %>% 
        pluck(.day) %>% 
        mutate(
          Patch = patch_count,
          Time = 
            str_c(date, sunrise) %>% 
            {
              ymd_hm(.) + 
                minutes(40 * (patch_order - 1))
            } %>% 
            format("%H:%M")
        ) %>% 
      select(
        Time,
        Patch = patch_count,
        Coverboards = boards,
        `Check nests` = check_nests,
        `Predator cameras` = predator_cameras
      ) %>% 
      kable(
        align =
          c(
            "c",
            "l",
            "c",
            "l"
          )
      ) %>% 
      my_kable_style()
  }

# Nest searching order:

nest_searching_order <-
  function(.day) {
    schedule_list %>%
      pluck(.day) %>%
      filter(patch_order != 1) %>%
      arrange(
        desc(patch_order)
      ) %>%
      pull(patch_count) %>%
      str_flatten(collapse = " \u2192 ")
  }

nest_searching <- 
  function(
    .day = "Tue",
    .helper_patch_1 = "-",
    .me_patch_1 = "-",
    .helper_patch_2 = "-",
    .me_patch_2 = "-"
  ) {
    start <- 
      schedule_list %>% 
      pluck(.day) %>% 
      filter(patch_order != 1) %>% 
      arrange(
        desc(patch_order)
      ) %>% 
      select(helper, patch_count) %>% 
      mutate(
        patch_count =
          factor(
            patch_count,
            levels = 
              patch_count
          )
      )
    
    crossing(
      Patch = start$patch_count,
      Person = 
        c(
          "TNS",
          pull(start, unique(helper))
        )
    ) %>% 
      mutate(
        Activities = 
          c(
            .helper_patch_1,
            .me_patch_1,
            .helper_patch_2,
            .me_patch_2
          )
      ) %>% 
      filter(
        Person != "-"
      ) %>% 
      kable() %>% 
      # my_kable_style() %>% 
      collapse_rows(
        columns = 1
      )
  }
```

```{css}

body {
  font-family: "Times New Roman", Times, serif;
  font-size: 16px;
}

.summary_box {
  margin-bottom: 1.5em;
}

.cell {
  margin-top: 0em;
  margin-bottom: 1em;
}

h1 {
  font-size: 1.5rem;
}

h2 {
  font-size: 1.15rem;
}

p {
  margin-bottom: 0;
}

h1, h2 {
  border-bottom: 1px solid #ccc;
  padding-bottom: 0;
  margin-bottom: 0.2em;
}

hr {
  padding-top: 20px;
  margin-top: 20px;
}

/* Accordion style */

.accordion {
  margin-top: 4px;
  background-color: #e6f0ff;
  color: #000000;
  cursor: pointer;
  padding: 18px;
  width: 100%;
  border-style: solid;
  border-width: 2px;
  border-color: #ffffff;
  text-align: left;
  outline: none;
  font-size: 1.15em;
  transition: 0.4s;
}

/* When you hover your mouse over the accordion button, it changes color. */

.active, .accordion:hover {
  background-color: #80b3ff; 
  color: #ffffff;
  font-weight: bold;
}

/* This is where the content of the accordion is placed. */

.panel {
  padding: 4px 4px;
  margin-top: 1em;
  margin-bottom: 1em;
  display: none;
  background-color: #fff;
  overflow: hidden;
}
```

# Weekly schedule: `r pretty_date_range(schedule)`

<button class="accordion">Monday `r day_level_data$Mon$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Mon$helper)`*

```{r}
morning_times(.day = "Mon")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Mon")
```

**Nest searching**: `r nest_searching_order(.day = "Mon")`

```{r}
nest_searching(
  .day = "Mon",
  .me_patch_1 = "Continue path from trailcam_0 to the northwest passage",
  .me_patch_2 = "Machete-search near coverboards 1 and 2"
)
```

:::

<button class="accordion">Tuesday `r day_level_data$Tue$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Tue$helper)`*

```{r}
morning_times(.day = "Tue")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Tue")
```

**Nest searching**: `r nest_searching_order(.day = "Tue")`

```{r}
nest_searching(
  .day = "Tue",
  .helper_patch_1 = "Search from board 5 to trailcam_1",
  .me_patch_1  = "Machete-search from board 2 to 3",
  .helper_patch_2 = "Search the Eastern half of the patch (machete optional)",
  .me_patch_2 = "Machete-search the Western half of the patch"
)
```

:::

<button class="accordion">Wednesday `r day_level_data$Wed$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Wed$helper)`*

```{r}
morning_times(.day = "Wed")
```

:::

**Point count times, coverboards, and nests to check**:

*BSE: Machete a trail at firehouse that connects trailcam_1 and the northwest passage. There is a fence near trailcam_1 that can be navigated around, but bring boltcutters just in case.*

```{r}
pred_counts(.day = "Wed")
```

**Nest searching**: forest_a &#8594; grassland_b
<!-- `r nest_searching_order(.day = "Wed")` -->

```{r}
# nest_searching(
#   .day = "Wed",
  # .me_patch_1,
  # .me_patch_2
# )

crossing(
  Patch = c("forest_a", "grassland_b"),
  Person = c("BSE", "TNS")
) %>% 
  mutate(
    Activities = 
      c(
        "Hunt down the catbirds and cardinals in the central island; Hunt the towhee near coverboard 6; Scan the stretch from coverboard 5 to 4",
        "Poison ivy island of coverboard 1; Scan the stretch from coverboard 4 to 5",
        "Install additional trailcams; Scan the stretch from coverboard 5 to 2 (macheteing along the way); Hunt the towhee near coverboard 3",
        "Install additional trailcams; Scan the stretch from trailcam_1 to coverboard 2 (macheteing along the way)"
      )
  ) %>% 
  kable() %>% 
  # my_kable_style() %>% 
  collapse_rows(
    columns = 1
  )
```

:::

<button class="accordion">Thursday `r day_level_data$Thu$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Thu$helper)`*

```{r}
morning_times(.day = "Thu")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Thu")
```

*Note: Install trailcam_2 at witch_hazel.*

**Nest searching**: firehouse &#8594; coyote
<!-- `r nest_searching_order(.day = "Thu")` -->

```{r}
# nest_searching(
#   .day = "Thu",
#   .helper_patch_1 = "Search the Western portion of the patch (near boards 1 and 2; machete optional)",
#   .me_patch_1  = "Install trailcam_2; Search the Western portion of the patch",
#   .helper_patch_2 = "Search the Northern half of the patch",
#   .me_patch_2 = "Rough chop along the Western edge; Create distributaries of the path from trailcam_1 to the northwest passage"
# )

crossing(
  Patch = c("firehouse", "coyote"),
  Person = c("CMS", "TNS")
) %>% 
  mutate(
    Activities = 
      c(
        "Search the Northern section of the patch (the area near trailcam_1 is thorny *gold*)",
        "Rough chop along the Western edge; Create distributaries of the path from trailcam_1 to the northwest passage",
        "SD card and batteries in trailcam 2; Explore areas around the machete network (machete optional)",
        "SD card and batteries in trailcam 2; Re-GPS path from CB 4 to CB 5; Continue machete network"
      )
  ) %>% 
  kable() %>% 
  # my_kable_style() %>% 
  collapse_rows(
    columns = 1
  )
```

*Note: There is an active nest right along the power line alley walkway at firehouse... be very careful when traversing through that area!*

:::

<button class="accordion">Friday `r day_level_data$Fri$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Fri$helper)`*

```{r}
morning_times(.day = "Fri")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Fri")
```

**Nest searching**: `r nest_searching_order(.day = "Fri")`

```{r}
nest_searching(
  .day = "Fri",
  .me_patch_1 = "Continue path down the patch; investigate NOCA and EATO pairs seen between CB 1 and CB 2; Change batteries and SD cards in cams 1 and 2",
  .me_patch_2 = "Continue path from CB 3 to CB 2; investigate NOCA activity between CB 4 and CB 5"
)
```

:::

<button class="accordion">Saturday `r day_level_data$Sat$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Sat$helper)`*

```{r}
morning_times(.day = "Sat")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Sat")
```

**Nest searching**: `r nest_searching_order(.day = "Sat")`

```{r}
nest_searching(
  .day = "Sat",
  # .me_patch_1,
  # .helper_patch_1,
  # .me_patch_2,
  # .helper_patch_2
)
```

:::

<script>
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
  acc[i].addEventListener("click", function() {
  this.classList.toggle("active");
  var panel = this.nextElementSibling;
  if (panel.style.display === "block") {
    panel.style.display = "none";
  } else {
    panel.style.display = "block";
  }
  });
}

// Expand the button for today's date by default:

var today = new Date().toLocaleDateString('en-GB', {
 day: 'numeric',
 month: 'long'
})

for (i = 0; i < acc.length; i++) {
  if (acc[i].textContent.includes(today)) {
    acc[i].classList.add("active");
    acc[i].nextElementSibling.style.display = "block";
    break;
  }
}

</script>
