---
format: html
pagetitle: schedule
editor: source
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
  message: false
---

```{r}

library(kableExtra)
library(glue)
library(here)
library(tidyverse)

here("scripts/functions.R") %>% 
  source()

weather <- 
  here("data/weather.rds") %>% 
  read_rds() %>% 
  mutate(
    day = wday(start_time, label = TRUE),
    .before = start_time
  ) %>% 
  select(
    day,
    temperature:hourly
  ) %>% 
  split(
    pull(., day)
  )

high_nests <-
  here("data", "field_data.rds") %>% 
  read_rds() %>% 
  pluck("nests") %>% 
  filter(height > 2) %>% 
  pull(nest_id) %>% 
  str_c(collapse = "|") %>% 
  str_c("(", ., ")")

next_nest_checks <-
  here("data", "temp_nest_checking.rds") %>% 
  read_rds() %>% 
  mutate(
    check_nests = 
      str_replace_all(
        check_nests,
        high_nests,
        "\\1 \U1F992"
      )
  )

next_pred_cam_maintenance <-
  here("data", "predator_camera_maintenance.rds") %>% 
  read_rds() %>% 
  mutate(
    patch,
    date = next_maintenance,
    camera_id = 
      str_extract_all(camera_id, "[0-2]$"),
    .keep = "none"
  ) %>% 
  summarize(
    predator_cameras = 
      str_flatten(camera_id, collapse = ", "),
    .by = !camera_id
  )

schedule <-
  here("data", "season_schedule.rds") %>% 
  read_rds() %>% 
  unnest(patch_counts) %>% 
  unnest(boards) %>% 
  filter(
    week ==
      week(
        today() + 1
      ) - 19,
  ) %>% 
  summarize(
    boards = 
      str_flatten(board_id, collapse = ", "),
    .by = !board_id
  ) %>% 
  left_join(
    next_nest_checks,
    by = join_by(date == date, patch_count == patch)
  ) %>% 
  left_join(
    next_pred_cam_maintenance,
    by = join_by(date, patch_count == patch)
  ) %>% 
  mutate(
    home_departure_time = 
      (
        hm(arrive) - minutes(45)
      ) %>% 
      hms::hms() %>% 
      as.character() %>% 
      str_remove(":00$"),
    scbi_departure_time =
      (
        hm(arrive) + hours(9)
      ) %>% 
      period_to_seconds() %>% 
      hms::as_hms() %>% 
      as.character() %>% 
      str_remove(":00$"),
    across(
      check_nests:predator_cameras,
      ~ replace_na(.x, "-")
    )
  )

schedule_list <-
  schedule %>% 
  split(schedule$day)

day_level_data <-
  schedule_list %>% 
  map(
    ~ .x %>% 
      select(
        date,
        arrive:helper
      ) %>% 
      distinct() %>% 
      mutate(
        date_pretty = make_pretty_dates(date)
      )
  )

# custom functions --------------------------------------------------------

my_kable_style <-
  function(.kable) {
    .kable %>% 
      kable_styling(
        bootstrap_options = 
          c(
            "striped",
            "hover",
            "condensed"
          ),
        full_width = FALSE,
        font_size = 28
      )
  }

# Departure, arrival, and sunrise table:

morning_times <- 
  function(.day) {
    schedule_list %>% 
      pluck(.day) %>% 
      distinct(
        "Home departure" = home_departure_time, 
        "Arrival" = arrive, 
        "Sunrise" = sunrise,
        "SCBI departure" = scbi_departure_time
      ) %>% 
      kable(
        format = "html",
        align = 
          c("c", "c", "c")
      ) %>% 
      my_kable_style() %>% 
      column_spec(1:3, width = "14.5em")
  }

# Format point counts and coverboards for a given day:

pred_counts <- 
  function(.day) {
    schedule_list %>% 
      pluck(.day) %>% 
      mutate(
        Patch = patch_count,
        Time = 
          str_c(date, sunrise) %>% 
          {
            ymd_hm(.) + 
              minutes(40 * (patch_order - 1))
          } %>% 
          format("%H:%M")
      ) %>% 
      select(
        Time,
        Patch = patch_count,
        Coverboards = boards,
        `Check nests` = check_nests,
        `Predator cameras` = predator_cameras
      ) %>% 
      kable(
        format = "html",
        align =
          c(
            "c",
            "l",
            "c",
            "l"
          )
      ) %>% 
      my_kable_style()
  }

# Nest searching order:

nest_searching_order <-
  function(
    .day,
    .ordered = TRUE,
    .patches
  ) {
    if(.ordered) {
      schedule_list %>%
        pluck(.day) %>%
        filter(patch_order != 1) %>%
        arrange(
          desc(patch_order)
        ) %>%
        pull(patch_count) %>%
        str_flatten(collapse = " \u2192 ")
    } else {
      .patches %>% 
        str_flatten(collapse = " \u2192 ")
    }
  }

# Nest searching activity details:

nest_searching <- 
  function(
    .day = "Tue",
    .ordered = TRUE,
    .helper,
    .patches,
    .helper_patch_1 = "-",
    .me_patch_1 = "-",
    .helper_patch_2 = "-",
    .me_patch_2 = "-"
  ) {
    if(.ordered) {
      start <- 
        schedule_list %>% 
        pluck(.day) %>% 
        filter(patch_order != 1) %>% 
        arrange(
          desc(patch_order)
        ) %>% 
        select(helper, patch_count) %>% 
        mutate(
          patch_count =
            factor(
              patch_count,
              levels = 
                patch_count
            )
        )
    } else {
      start <- 
        tibble(
          helper = .helper,
          patch_count = .patches
        ) %>% 
        mutate(
          patch_count =
            factor(
              patch_count,
              levels = 
                patch_count
            )
        )
    }
    
    crossing(
      Patch = start$patch_count,
      Person = 
        c(
          "TNS",
          pull(start, unique(helper))
        )
    ) %>% 
      mutate(
        Activities = 
          c(
            .helper_patch_1,
            .me_patch_1,
            .helper_patch_2,
            .me_patch_2
          )
      ) %>% 
      filter(
        Person != "-"
      ) %>% 
      kable() %>% 
      # my_kable_style() %>% 
      collapse_rows(
        columns = 1
      )
  }
```

```{css}

body {
font-family: "Times New Roman", Times, serif;
font-size: 16px;
}

.summary_box {
margin-bottom: 1.5em;
}

.cell {
margin-top: 0em;
margin-bottom: 1em;
}

h1 {
font-size: 1.5rem;
}

h2 {
font-size: 1.15rem;
}

p {
margin-bottom: 0;
}

h1, h2 {
border-bottom: 1px solid #ccc;
padding-bottom: 0;
margin-bottom: 0.2em;
}

hr {
padding-top: 20px;
margin-top: 20px;
}

/* Accordion style */

.accordion {
margin-top: 4px;
background-color: #e6f0ff;
color: #000000;
cursor: pointer;
padding: 18px;
width: 100%;
border-style: solid;
border-width: 2px;
border-color: #ffffff;
text-align: left;
outline: none;
font-size: 1.15em;
transition: 0.4s;
}

/* When you hover your mouse over the accordion button, it changes color. */

.active, .accordion:hover {
background-color: #80b3ff; 
color: #ffffff;
font-weight: bold;
}

/* This is where the content of the accordion is placed. */

.panel {
padding: 4px 4px;
margin-top: 1em;
margin-bottom: 1em;
display: none;
background-color: #fff;
overflow: hidden;
}
```

# Weekly schedule: `r pretty_date_range(schedule)`

<button class="accordion">Monday `r day_level_data$Mon$date_pretty`</button>

::: panel

*Helper: `r unique(schedule_list$Mon$helper)`*

::: summary_box

```{r}
morning_times(.day = "Mon")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Mon")
```

**Nest searching**: `r nest_searching_order(.day = "Mon")`

```{r}
nest_searching(
  .day = "Mon",
  .me_patch_1 = "Finish and GPS path from trailcam_2 to CB 3; Create distributaries from the central N-S path",
  .me_patch_2 = "Search near CB 1 and 2 -- carve paths where necessary",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .patches = c("", ""),
  # .helper = "",
  # .helper_patch_1 = "-",
  # .helper_patch_2 = "-"
)
```

<button class="accordion" style="font-size: 1em; font-weight: 500; padding: 5;">

**Weather**: `r weather$Mon$detailed_forecast`

```{r}

weather$Mon %>% 
  mutate(
    `High temperature` = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

</button>

::: panel

```{r}

weather$Mon %>% 
  select(day, hourly) %>% 
  unnest(hourly) %>% 
  filter(
    hour(start_time) >= 4,
    hour(start_time) <= 17
  ) %>% 
  mutate(
    Time = 
      hms::as_hms(start_time) %>% 
      as.character() %>% 
      str_remove(":00$"),
    Forecast = short_forecast,
    Temperature = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

:::

:::

<button class="accordion">Tuesday `r day_level_data$Tue$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Tue$helper)`*

```{r}
morning_times(.day = "Tue")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Tue")
```

**Nest searching**: `r nest_searching_order(.day = "Tue")`

```{r}
nest_searching(
  .day = "Tue",
  .helper_patch_1 = "Explore the Northern section of the cross-patch path",
  .me_patch_1 = "Finish and GPS the Southern section of the cross-patch path; Hunt for catbirds and cardinals in the Southern dense Autumn olive",
  .helper_patch_2 = "Between CB 4 and 6 (I've heard some serious cardinal activity there)",
  .me_patch_2 = "Machete-explore between CB 1 and 2",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .helper = "",
  # .patches = c("", "")
)
```

<button class="accordion" style="font-size: 1em; font-weight: 500; padding: 5;">

**Weather**: `r weather$Tue$detailed_forecast`

```{r}

weather$Tue %>% 
  mutate(
    `High temperature` = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

</button>

::: panel

```{r}

weather$Tue %>% 
  select(day, hourly) %>% 
  unnest(hourly) %>% 
  filter(
    hour(start_time) >= 4,
    hour(start_time) <= 17
  ) %>% 
  mutate(
    Time = 
      hms::as_hms(start_time) %>% 
      as.character() %>% 
      str_remove(":00$"),
    Forecast = short_forecast,
    Temperature = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

:::

:::

<button class="accordion">Wednesday `r day_level_data$Wed$date_pretty`</button>

::: panel

::: summary_box

*Helper: BSE*
<!-- `r unique(schedule_list$Wed$helper)`* -->

```{r}
morning_times(.day = "Wed")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Wed")
```

*BSE: Machete (and search) at firehouse: Bramble patch past coverboard 1, trailcam_1 area (locate, gps, and flag path to CB 3)*

**Nest searching**: `r nest_searching_order(.day = "Wed")`

```{r}
nest_searching(
  .day = "Wed",
  .me_patch_1 = "Machete-search from CB 6 to CB 4 (and beyond)",
  .me_patch_2 = "CB 3 outcrop, working towards CB 6",
  
  # If schedule changes:
  
  .ordered = FALSE,
  .patches = c("leech", "grassland_b"),
  .helper = "BSE",
  .helper_patch_1 = "Bramble pocket past the entrance gate",
  .helper_patch_2 = "Southern section of the patch (inside and around the trail circle)"
)
```

<button class="accordion" style="font-size: 1em; font-weight: 500; padding: 5;">

**Weather**: `r weather$Wed$detailed_forecast`

```{r}

weather$Wed %>% 
  mutate(
    `High temperature` = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

</button>

::: panel

```{r}

weather$Wed %>% 
  select(day, hourly) %>% 
  unnest(hourly) %>% 
  filter(
    hour(start_time) >= 4,
    hour(start_time) <= 17
  ) %>% 
  mutate(
    Time = 
      hms::as_hms(start_time) %>% 
      as.character() %>% 
      str_remove(":00$"),
    Forecast = short_forecast,
    Temperature = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

:::

:::

<button class="accordion">Thursday `r day_level_data$Thu$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Thu$helper)`*

```{r}
morning_times(.day = "Thu")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Thu")
```

**Nest searching**: `r nest_searching_order(.day = "Thu")`

```{r}
nest_searching(
  .day = "Thu",
  .helper_patch_1 = "-",
  .me_patch_1 = "Create branches off the CB 1 to CB 3 path",
  .helper_patch_2 = "Explore the Western section of the patch (there's a new trail at the Western edge)",
  .me_patch_2 = "Inlets along the Northern edge",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .helper = "",
  # .patches = c("", "")
)
```

Notes: 

* Alternate activity: At each nest, take a picture from further away, circle the nest in the picture, and jot down a brief description of where the picture was taken in relation to the nest. Also record the status of the nest (e.g., How old is it? If recent, would it be a good candidate for fake, Quinn-poop-covered eggs?)
* Install a metal box at witch_hazel trailcam_0

<button class="accordion" style="font-size: 1em; font-weight: 500; padding: 5;">

**Weather**: `r weather$Thu$detailed_forecast`

```{r}

weather$Thu %>% 
  mutate(
    `High temperature` = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

</button>

::: panel

```{r}

weather$Thu %>% 
  select(day, hourly) %>% 
  unnest(hourly) %>% 
  filter(
    hour(start_time) >= 4,
    hour(start_time) <= 17
  ) %>% 
  mutate(
    Time = 
      hms::as_hms(start_time) %>% 
      as.character() %>% 
      str_remove(":00$"),
    Forecast = short_forecast,
    Temperature = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

:::

:::

<button class="accordion">Friday `r day_level_data$Fri$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Fri$helper)`*

```{r}
morning_times(.day = "Fri")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Fri")
```

**Nest searching**: `r nest_searching_order(.day = "Fri")`

```{r}
nest_searching(
  .day = "Fri",
  .me_patch_1 = "Focus on the Western section (CB 6 end)",
  .me_patch_2 = "Continue to create distributaries along the main paths; Investigate more near trailcam_1",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .patches = c("", ""),
  # .helper = "-",
  # .helper_patch_1 = "",
  # .helper_patch_2 = ""
)
```

Notes:

* At each nest, take a picture from further away and jot down a brief description of where the picture was taken and how to find the nest.
* Only change batteries and SD cards at one trailcam per patch (to avoid future maintenance scheduling woes).
* Take note of which inactive nests might be suitable for artificial eggs.

<button class="accordion" style="font-size: 1em; font-weight: 500; padding: 5;">

**Weather**: `r weather$Fri$detailed_forecast`

```{r}

weather$Fri %>% 
  mutate(
    `High temperature` = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

</button>

::: panel

```{r}

weather$Fri %>% 
  select(day, hourly) %>% 
  unnest(hourly) %>% 
  filter(
    hour(start_time) >= 4,
    hour(start_time) <= 17
  ) %>% 
  mutate(
    Time = 
      hms::as_hms(start_time) %>% 
      as.character() %>% 
      str_remove(":00$"),
    Forecast = short_forecast,
    Temperature = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

:::

:::

<button class="accordion">Saturday `r day_level_data$Sat$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Sat$helper)`*

```{r}
morning_times(.day = "Sat")
```

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Sat")
```

*BSE: Machete-search from trailcam_2 to CB 1 in grassland_a during morning sampling.*

**Nest searching**: `r nest_searching_order(.day = "Sat")`

```{r}
nest_searching(
  .day = "Sat",
  .helper_patch_1 = "CB 5 to 4",
  .me_patch_1 = "Bamboo patch area and CB 4 to 5",
  .helper_patch_2 = "Continue exploring around the pocket along entrace path",
  .me_patch_2 = "Continue exploring near CB 6 and the edges along the power line alleyway",
  
  # If schedule changes:
  
  # .ordered = FALSE,
  # .helper = "-",
  # .patches = c("leech", "grassland_b")
)
```

Notes:

* At each nest, take a picture from further away and jot down a brief description of where the picture was taken and how to find the nest.
* Take note of which inactive nests might be suitable for artificial eggs.

<button class="accordion" style="font-size: 1em; font-weight: 500; padding: 5;">

**Weather**: `r weather$Sat$detailed_forecast`

```{r}

weather$Sat %>% 
  mutate(
    `High temperature` = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

</button>

::: panel

```{r}

weather$Sat %>% 
  select(day, hourly) %>% 
  unnest(hourly) %>% 
  filter(
    hour(start_time) >= 4,
    hour(start_time) <= 17
  ) %>% 
  mutate(
    Time = 
      hms::as_hms(start_time) %>% 
      as.character() %>% 
      str_remove(":00$"),
    Forecast = short_forecast,
    Temperature = temperature,
    `Chance of rain` = 
      probability_of_precipitation_percent %>% 
      str_c("%"),
    .keep = "none"
  ) %>% 
  kable(
    format = "html",
    align =
      c(
        "c",
        "c"
      )
  ) %>% 
  my_kable_style()

```

:::

:::

<script>
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
acc[i].addEventListener("click", function() {
this.classList.toggle("active");
var panel = this.nextElementSibling;
if (panel.style.display === "block") {
panel.style.display = "none";
} else {
panel.style.display = "block";
}
});
}

// Expand the button for today's date by default:

var today = new Date().toLocaleDateString('en-GB', {
day: 'numeric',
month: 'long'
})

for (i = 0; i < acc.length; i++) {
if (acc[i].textContent.includes(today)) {
acc[i].classList.add("active");
acc[i].nextElementSibling.style.display = "block";
break;
}
}

</script>
