---
format: html
pagetitle: schedule
editor: source
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
  message: false
---

```{r}

library(kableExtra)
library(glue)
library(here)
library(tidyverse)

here("scripts/functions.R") %>% 
  source()

next_nest_checks <-
  here("data", "temp_nest_checking.rds") %>% 
  read_rds()

schedule <- 
  here("data", "season_schedule.rds") %>% 
  read_rds() %>% 
  unnest(patch_counts) %>% 
  unnest(boards) %>% 
  filter(
    week ==
        week(
        today() + 1
      ) - 19,
  ) %>% 
  summarize(
    boards = 
      str_flatten(board_id, collapse = ", "),
    .by = !board_id
  ) %>% 
  left_join(
    next_nest_checks,
    by = join_by(date == date, patch_count == patch)
  ) %>% 
  mutate(
    departure_time = 
      (
        hm(arrive) - minutes(45)
      ) %>% 
      hms::hms() %>% 
      as.character() %>% 
      str_remove(":00$"),
    check_nests = replace_na(check_nests, "-")
  )

schedule_list <-
  schedule %>% 
  split(schedule$day)

day_level_data <-
  schedule_list %>% 
  map(
    ~ .x %>% 
      select(
          date,
          arrive:helper
        ) %>% 
        distinct() %>% 
      mutate(
        date_pretty = make_pretty_dates(date)
      )
  )

# custom functions --------------------------------------------------------

my_kable_style <-
  function(.kable) {
    .kable %>% 
      kable_styling(
        bootstrap_options = 
          c(
            "striped",
            "hover",
            "condensed"
          ),
        full_width = FALSE,
        font_size = 28
      )
  }

# Format point counts and coverboards for a given day:

pred_counts <- 
  function(.day) {
      schedule_list %>% 
        pluck(.day) %>% 
        mutate(
          Patch = patch_count,
          Time = 
            str_c(date, sunrise) %>% 
            {
              ymd_hm(.) + 
                minutes(40 * (patch_order - 1))
            } %>% 
            format("%H:%M")
        ) %>% 
      select(
        Time,
        Patch = patch_count,
        Coverboards = boards,
        `Check nests` = check_nests
      ) %>% 
      kable(
        align =
          c(
            "c",
            "l",
            "c",
            "l"
          )
      ) %>% 
      my_kable_style()
  }

# Nest searching order:

nest_searching <- 
  function(.day) {
    schedule_list %>% 
      pluck(.day) %>% 
      arrange(
        desc(patch_order)
      ) %>% 
      pull(patch_count) %>% 
      str_flatten(collapse = " \u2192 ")
  }
```

```{css}

body {
  font-family: "Times New Roman", Times, serif;
  font-size: 16px;
}

.summary_box {
  margin-bottom: 1.5em;
}

.cell {
  margin-top: 0em;
  margin-bottom: 1em;
}

h1 {
  font-size: 1.5rem;
}

h2 {
  font-size: 1.15rem;
}

p {
  margin-bottom: 0;
}

h1, h2 {
  border-bottom: 1px solid #ccc;
  padding-bottom: 0;
  margin-bottom: 0.2em;
}

hr {
  padding-top: 20px;
  margin-top: 20px;
}

/* Accordion style */

.accordion {
  margin-top: 4px;
  background-color: #e6f0ff;
  color: #000000;
  cursor: pointer;
  padding: 18px;
  width: 100%;
  border-style: solid;
  border-width: 2px;
  border-color: #ffffff;
  text-align: left;
  outline: none;
  font-size: 1.15em;
  transition: 0.4s;
}

/* When you hover your mouse over the accordion button, it changes color. */

.active, .accordion:hover {
  background-color: #80b3ff; 
  color: #ffffff;
  font-weight: bold;
}

/* This is where the content of the accordion is placed. */

.panel {
  padding: 4px 4px;
  margin-top: 1em;
  margin-bottom: 1em;
  display: none;
  background-color: #fff;
  overflow: hidden;
}
```

# Weekly schedule: `r pretty_date_range(schedule)`

::: summary_box

We will arrive at dawn to have time for set-up and travel to the point count location. The first point count starts at sunrise. We will arrive at the point count location a few minutes before then to let the birds settle down before beginning.

:::

<button class="accordion">Monday `r day_level_data$Mon$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Mon$helper)`*

**Departure**: `r unique(schedule_list$Mon$departure_time)`

**Arrival**: `r unique(schedule_list$Mon$arrive)`

**Sunrise**: `r unique(schedule_list$Mon$sunrise)`

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Mon")
```

**Nest searching**: `r nest_searching(.day = "Mon")`

:::

<button class="accordion">Tuesday `r day_level_data$Tue$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Tue$helper)`*

**Departure**: `r unique(schedule_list$Tue$departure_time)`

**Arrival**: `r unique(schedule_list$Tue$arrive)`

**Sunrise**: `r unique(schedule_list$Tue$sunrise)`

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Tue")
```

**Nest searching**: `r nest_searching(.day = "Tue")`

:::

<button class="accordion">Wednesday `r day_level_data$Wed$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Wed$helper)`*

**Departure**: `r unique(schedule_list$Wed$departure_time)`

**Arrival**: `r unique(schedule_list$Wed$arrive)`

**Sunrise**: `r unique(schedule_list$Wed$sunrise)`

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Wed")
```

**Nest searching**: `r nest_searching(.day = "Wed")`

:::

<button class="accordion">Thursday `r day_level_data$Thu$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Thu$helper)`*

**Departure**: `r unique(schedule_list$Thu$departure_time)`

**Arrival**: `r unique(schedule_list$Thu$arrive)`

**Sunrise**: `r unique(schedule_list$Thu$sunrise)`

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Thu")
```

**Nest searching**: `r nest_searching(.day = "Thu")`

:::

<button class="accordion">Friday `r day_level_data$Fri$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Fri$helper)`*

**Departure**: `r unique(schedule_list$Fri$departure_time)`

**Arrival**: `r unique(schedule_list$Fri$arrive)`

**Sunrise**: `r unique(schedule_list$Fri$sunrise)`

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Fri")
```

**Nest searching**: `r nest_searching(.day = "Fri")`

:::

<button class="accordion">Saturday `r day_level_data$Sat$date_pretty`</button>

::: panel

::: summary_box

*Helper: `r unique(schedule_list$Fri$helper)`*

**Departure**: `r unique(schedule_list$Sat$departure_time)`

**Arrival**: `r unique(schedule_list$Sat$arrive)`

**Sunrise**: `r unique(schedule_list$Sat$sunrise)`

:::

**Point count times, coverboards, and nests to check**:

```{r}
pred_counts(.day = "Sat")
```

**Nest searching**: `r nest_searching(.day = "Sat")`

:::

<script>
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
  acc[i].addEventListener("click", function() {
  this.classList.toggle("active");
  var panel = this.nextElementSibling;
  if (panel.style.display === "block") {
    panel.style.display = "none";
  } else {
    panel.style.display = "block";
  }
  });
}

// Expand the button for today's date by default:

var today = new Date().toLocaleDateString('en-GB', {
 day: 'numeric',
 month: 'long'
})

for (i = 0; i < acc.length; i++) {
  if (acc[i].textContent.includes(today)) {
    acc[i].classList.add("active");
    acc[i].nextElementSibling.style.display = "block";
    break;
  }
}

</script>
